---
title: "R Scripts"
author: "Hemachandra Ghanta <br /> Ayesha Ruhi Damda <br />Jeremy Reep"
date: "October 30, 2018"
output:
  html_document:
    theme: cosmo
    toc: yes
  github_document:
    toc: yes
  word_document: default
  pdf_document:
    toc: yes
---
* * *
# Summary on the Scripts
The structure of the skink data set shows there are three values 0, 1, 2, NA. Although the data looks quantitative, it is actually qualitative with:
0 representing - no traces found
1 representing - traces found
2 representing - sand skinks found
NA representing - no observations made

The water data is much more straight forward. For each day, there are a series of observations measuring the levels of a number of water-borne particulates. The current observation variables are total nitrogen and total phosphorus. The goal is to track the decline in particulates as the water moves through the waterbody. Basic statistics are useful to help understand the data, but most of the analysis will be within the coming plots. The code for the water data will be after the code for the sand skink data.

```{r clpData}
clpData <- read.csv("F:/UNO/Fall 2018/8086-Data to Decisions/Polk Co Parks/Data/SS_Crooked Lake Sandhil.csv", header = TRUE)
str(clpData)
```


So in this case finding the average, max, min is not useful. Hence we continued to find the count of 0's, 1's, 2's for each year to get the number of sand skinks found/not found in each year.

## Crooked Lake Sandhil area

Below is the summary on sand skinks in Crooked Lake Sandhil area.

### 2006

```{r Summary2006, echo=FALSE}
library(plyr)
clp2006 <- data.frame(y2006 = c(clpData[,"X4.6.2006"], clpData[,"X4.13.2006"], clpData[,"X4.13.2006"],
                                clpData[,"X4.13.2006"], clpData[,"X4.13.2006"], clpData[,"X4.13.2006"],
                                clpData[,"X4.13.2006"], clpData[,"X4.13.2006"]))
count(clp2006, vars = "y2006")
```
Inference: 116 not found, 75 traces found, 1 found

### 2011
```{r}
clp2011 <- data.frame(y2011 = c(clpData[,"X4.7.2011"], clpData[,"X4.14.2011"], clpData[,"X4.21.2011"],
                                clpData[,"X4.28.2011"], clpData[,"X5.5.2011"], clpData[,"X5.12.2011"],
                                clpData[,"X5.19.2011"], clpData[,"X5.26.2011"]))
count(clp2011, vars = "y2011")
```
Inference: 119 not found, 49 traces, 24 No observations 

### 2012
```{r}
clp2012 <- data.frame(y2012 = c(clpData[,"X4.5.2012"], clpData[,"X4.12.2012"], clpData[,"X4.19.2012"],
                                clpData[,"X4.26.2012"], clpData[,"X5.3.2012"], clpData[,"X5.10.2012"],
                                clpData[,"X5.17.2012"], clpData[,"X5.24.2012"]))
count(clp2012, vars = "y2012")
```
Inference: 113 not found, 79 traces

### 2013
```{r}
clp2013 <- data.frame(y2013 = c(clpData[,"X4.4.2013"], clpData[,"X4.11.2013"], clpData[,"X4.18.2013"],
                                clpData[,"X4.25.2013"], clpData[,"X5.2.2013"], clpData[,"X5.19.2013"],
                                clpData[,"X5.23.2013"], clpData[,"X5.30.2013"]))
count(clp2013, vars = "y2013")
```
Inference: 113 not found, 61 traces

### 2014
```{r}
clp2014 <- data.frame(y2014 = c(clpData[,"X4.3.2014"], clpData[,"X4.10.2014"], clpData[,"X4.24.2014"],
                                clpData[,"X5.1.2014"], clpData[,"X5.8.2014"], clpData[,"X5.22.2014"],
                                clpData[,"X5.29.2014"], clpData[,"X6.5.2014"]))
count(clp2014, vars = "y2014")
```
Inference: 155 not found, 37 traces

### 2015
```{r}
clp2015 <- data.frame(y2015 = c(clpData[,"X4.7.2015"], clpData[,"X4.9.2015"], clpData[,"X4.16.2015"],
                                clpData[,"X4.23.2015"], clpData[,"X4.30.2015"], clpData[,"X5.14.2015"],
                                clpData[,"X5.21.2015"], clpData[,"X5.28.2015"]))
count(clp2015, vars = "y2015")
```
Inference: 153 not found, 39 traces

### 2016
```{r}
clp2016 <- data.frame(y2016 = c(clpData[,"X4.7.2016"], clpData[,"X4.14.2016"], clpData[,"X4.21.2016"],
                                clpData[,"X4.28.2016"], clpData[,"X5.5.2016"], clpData[,"X5.12.2016"],
                                clpData[,"X5.19.2016"], clpData[,"X5.26.2016"]))
count(clp2016, vars = "y2016")
```
Inference: 153 not found, 38 traces, 1 found

### 2017
```{r}
clp2017 <- data.frame(y2017 = c(clpData[,"X4.20.2017"], clpData[,"X4.27.2017"], clpData[,"X5.4.2017"],
                                clpData[,"X5.11.2017"], clpData[,"X5.18.2017"], clpData[,"X5.25.2017"]))
count(clp2017, vars = "y2017")
```
Inference: 72 not found, 70 traces, 2 not observed

### 2018
```{r}
clp2018 <- data.frame(y2018 = c(clpData[,"X4.5.2018"], clpData[,"X4.12.2018"], clpData[,"X4.19.2018"],
                                clpData[,"X4.26.2018"], clpData[,"X5.3.2018"], clpData[,"X5.10.2018"],
                                clpData[,"X5.17.2018"], clpData[,"X5.24.2018"]))
count(clp2018, vars = "y2018")
```
Inference: 126 not found, 54 traces, 11 found

## Water Data

```{r wtrData}
wtrData <- read.csv("WaterDataClean.csv", header = TRUE)
str(wtrData)
```

### Analysis for Total Nitrogen

```{r nitroClean}
nitro <- sqldf('SELECT * FROM wtr WHERE Parameter LIKE "%nitrogen total%"')
nitroClean <- sqldf('SELECT * FROM nitro ORDER BY "Date.Collected", LabNo')
sqldf('SELECT "Date.Collected", AVG(Result) FROM nitroClean GROUP BY "Date.Collected"')
```
### Analysis for Total Nitrogen

```{r phosClean}
phos <- sqldf('SELECT * FROM wtr WHERE Parameter LIKE "%phosphorus total%"')
phosClean <- sqldf('SELECT * FROM phos ORDER BY "Date.Collected", LabNo')
sqldf('SELECT "Date.Collected", AVG(Result) FROM phosClean GROUP BY "Date.Collected"')
```